The Ranked Nearest Neighbour Interchange space

### 2019-07-15 paper.tex
minor

    Induction step: $l+1 \to l$\\
    Induction hypothesis: For each pair of caterpillar trees with caterpillar distance $l+1$ there is a shortest path between these trees that only consists of caterpillar trees, which means that the distance between these trees is $l+1$.
    Let $T$ and $R$ be caterpillar trees with caterpillar distance $l$.
    Since $l < \frac{(n-1)(n-2)}{2}$, there is one loop $k$ in the caterpillar path from $R$ to $T$ that is given $\csort$ where less than $n-2-k$ pairs taxa swap positions.
    It follows that there is a taxon $a$ that has parent with rank $n-2-k$ in $T$ and does not need to move all the way up starting at the cherry in loop $k$.
    Let $b$ be the taxon whose parent has rank one less than the parent of $a$ in the tree at the beginning of loop number $k$.
    We can assume without loss of generality that loop $k$ is the first loop in which the number of swaps is not maximal.
    It follows that $a$ and $b$ must be neighboured taxa in $R$.
    Let us no consider caterpillar tree $R'$ resulting from $R$ by exchanging taxa $a$ and $b$.
    It is clear that $R'$ has caterpillar distance $d_c(T,R') = d_c(T,R) + 1 = l+1$ to $T$ and moreover, $d(R,R') = 1$.
    Hence we can apply the induction hypothesis on $T$ and $R'$ and see that $d(T,R') = l+1$.
    If it were $d(T,R) < l$, we would have $d(T,R') \leq d(T,R) + d(R,R') < l + 1$ which contradicts the induction hypothesis.
    We can conclude $d(T,R) = l$, which completes the proof.
\end{proof}

>>>>

    Induction step: $l+1 \to l$\\
    Induction hypothesis: For each pair of caterpillar trees with caterpillar distance $l+1$ there is a shortest path between these trees that only consists of caterpillar trees, which means that the distance between these trees is $l+1$.
    Let $T$ and $R$ be caterpillar trees with caterpillar distance $l$.
    We consider the shortest caterpillar path computed by $\csort$.
    Since $l < \frac{(n-1)(n-2)}{2}$, there is one loop $k$ when running $\csort$ where less than $n-2-k$ pairs taxa swap positions.
    It follows that there is a taxon $a$ that has parent with rank $n-2-k$ in $T$ and does not need to move all the way up starting at the cherry in loop $k$.
    Let $b$ be the taxon whose parent has rank one less than the parent of $a$ in the tree at the beginning of loop number $k$.
    We can assume without loss of generality that loop $k$ is the first loop in which the number of swaps is not maximal.
    It follows that $a$ and $b$ must be neighboured taxa in $R$.
    Let us no consider caterpillar tree $R'$ resulting from $R$ by exchanging taxa $a$ and $b$.
    It is clear that $R'$ has caterpillar distance $d_c(T,R') = d_c(T,R) + 1 = l+1$ to $T$ and moreover, $d(R,R') = 1$.
    Hence we can apply the induction hypothesis on $T$ and $R'$ and see that $d(T,R') = l+1$.
    If it were $d(T,R) < l$, we would have $d(T,R') \leq d(T,R) + d(R,R') < l + 1$ which contradicts the induction hypothesis.
    We can conclude $d(T,R) = l$, which completes the proof.
\end{proof}
